Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-07 ICPP-19/communications.tex
minor

	\begin{algorithm}
		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
		\begin{algorithmic}[1]
			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
			\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
			\STATE Append $Q'$ to $Q$
			\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
			\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
			\WHILE{$Q \neq \emptyset$}
			\STATE remove a task $T$ from beginning of $Q$ for processing
			\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
			\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
			\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
			\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
			\ENDWHILE
		\end{algorithmic}
	\end{algorithm}

@@

	\begin{table*}[htb]
		\scriptsize
		\begin{tabular}{|c|p{3cm}|}
			\hline
			\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
			order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
			increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
			decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
			increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
			decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
			largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
			smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
			maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
			optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
			optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
			optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
		\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios}
	\end{table*}

>>>>

	\begin{algorithm}
		\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case).}
		\begin{algorithmic}[1]
			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
			\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
			\STATE Append $Q'$ to $Q$
			\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
			\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
			\WHILE{$Q \neq \emptyset$}
			\STATE remove a task $T$ from beginning of $Q$ for processing
			\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
			\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
			\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
			\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
			\ENDWHILE
		\end{algorithmic}
	\end{algorithm}

@@

	\begin{table*}[htb]
		\scriptsize
		\begin{tabular}{|c|p{3cm}|}
			\hline
			\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
			order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
			increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
			decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
			increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
			decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
			largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
			smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
			maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
			optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
			optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
			optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
		\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios.}
	\end{table*}
